---
title: "Carbon Bookkeeping"
author: "Arne Thiemann"
date: "`r Sys.Date()`"
output: html_document
---

in Baumann et al., 2017:

woodland = forests
pasture = grazing lands


##  Task 1

Prepare the table in way that you have the columns Year and Ecoregion as so-called grouping variables. Along with these variables, each of the land cover conversions should be stored in individual columns.

```{r}
library(tidyverse)

lcc_chaco <- read_csv("LCC_Chaco_Numbers_Updated.csv")

lcc_chaco_grouped <- lcc_chaco %>% 
  group_by(Year, Ecoregion) %>% 
  summarise(
    WL_P_km2 = sum(WL_P_km2), # woodland to pasture
    WL_C_km2 = sum(WL_C_km2), # woodland to cropland
    P_C_km2 = sum(P_C_km2) # pasture to cropland
  )
```

## Task 2

Implement a CBKM in R for the emissions from AGB loss.

```{r}
# import table from Baumann et al., 2017, p. 1906
land2carbon <- read_csv("land2carbon.csv")

# Creating three different versions, thankfully the data are quite simple, so we can work with min and max, for the IPCC parameters and the Houghton & Hackler version
land2carbon_par <- land2carbon %>%
  filter(variable == "Total carbon in Biomass") %>% 
  group_by(class, region) %>% 
  summarise(
    value_IPCC = min(value),
    value_HoughtonHackler = max(value),
    value_mean = mean(value)
  )

# create lookup table
lookup_table <- land2carbon_par %>% 
  crossing(from = class, to = class) %>% 
  mutate(
    identifier = paste(
      from, to, "km2", sep = "_"
    )
  )


lookup_table <- crossing(
  from = land2carbon_par$class,
  to = land2carbon_par$class,
  region = land2carbon_par$region) %>% 
  mutate(
    identifier = paste(
      from, to, "km2", sep = "_"
    ) %>% 
      str_replace_all(., c("Cropland" = "C", "Forest" = "WL", "Grazing lands" = "P"))
  ) %>% 
  left_join(
    land2carbon_par %>% select(class, region, value_mean),
    by = c("from" = "class", "region")
  ) %>% 
  left_join(
    land2carbon_par %>% select(class, region, value_mean),
    by = c("to" = "class", "region")
  ) %>% 
  mutate(value_mean = value_mean.y - value_mean.x) %>% 
  select(region, from, to, identifier, value_mean)


# now apply the lookup
lcc_chaco_carbon <- lcc_chaco_grouped %>% 
  pivot_longer(
    !c(Year, Ecoregion),
    names_to = "change_type",
    values_to = "km2"
  ) %>% 
  inner_join(
    lookup_table,
    by = c(
      "Ecoregion" = "region",
      "change_type" = "identifier"
    )
  ) %>% 
  mutate(
    carbon_flow = km2 * value_mean # check conversion and unit! Mg C / ha
  )
```


When you are done, calculate the total emissions from AGB loss for the three land-cover conversion types for the period 1986-2050.

```{r}
lcc_chaco_carbon %>% 
  group_by(change_type) %>% 
  summarise(carbon_emissions = sum(carbon_flow))
```


Visualize the results in a suitable way (e.g., in a line graph), and prepare this graph 
(a) for the entire Chaco, and 
(b) separated for the wet, dry, and very dry Chaco.

```{r}
ggplot(
  lcc_chaco_carbon,
  aes(
    Year,
    carbon_flow *-1,
    color = change_type
  )
) + facet_wrap(~Ecoregion) +
  geom_line()

ggplot(
  lcc_chaco_carbon,
  aes(
    Year,
    carbon_flow * -1,
    fill = change_type
  )
) + facet_wrap(~Ecoregion) +
  geom_area() +
  theme_light()

```


You are welcome to provide any other visualization (e.g., the different flows for one conversion type), but you do not have to. Have a look at the paper by Baumann et al. for an idea of visualizing emissions.

```{r}

```


What are the total emissions from land-cover change, aggregated over the period 1986-2025?

```{r}

```